Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
refine caption in dependency graph

In order to prove formally that the length of the
kind of hydra battles we consider is not given by any primitive recursive function, we chose to use a formalization of primitive recursive functions that was originally part of Russell O'Connor's formalization of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while straight-line boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories. Dotted lines represent Coq code ancestry, while regular lines represent direct code dependencies.}
  \label{fig:genealogy}
\end{figure}

>>>>

In order to prove formally that the length of the
kind of hydra battles we consider is not given by a primitive recursive function, we chose to use a formalization of the primitive recursive functions that was originally part of Russell O'Connor's formalization of G\"{o}del's first incompleteness theorem~\cite{OConnor05, Goedel}.
For this purpose, and above all in consideration of the scientific interest of this contribution, we decided to host and maintain O'Connor's work in \community.

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while regular boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories. Dotted lines represent Coq code ancestry, while regular lines represent direct code dependencies.}
  \label{fig:genealogy}
\end{figure}
